Computing Entropies with Nested Sampling

### 2017-10-16 talk/ms.tex
A figure

>>>>

% New slide
\begin{frame}
\frametitle{Shannon entropy}

Consider a discrete probability distribution with probabilities
$\boldsymbol{p} = \{p_i\}$. The Shannon entropy is
\begin{align}
H(\boldsymbol{p}) &= -\sum_i p_i \log p_i
\end{align}

It is a real-valued property of the distribution.

% New slide
\begin{frame}
\frametitle{Relative entropy}

Consider two discrete probability distributions with probabilities
$\boldsymbol{p} = \{p_i\}$ and $\boldsymbol{q} = \{q_i\}$.
The relative entropy is
\begin{align}
H(\boldsymbol{p}; \boldsymbol{q}) &= -\sum_i p_i \log\left(\frac{p_i}{q_i}\right)
\end{align}
Without the minus sign,
it's the `Kullback-Leibler divergence', and is more fundamental than the
Shannon entropy. With uniform $\boldsymbol{q}$, it reduces to the Shannon
entropy (up to an additive constant).
\end{frame}

% New slide
\begin{frame}
\frametitle{Entropy quantifies uncertainty}
If there are just $N$ equally likely possibilities,
i.e., $p_i = 1/N$, then $H = \log N$. \vspace{0.5em}

\begin{center}
\includegraphics[width=0.6\textwidth]{entropy1.pdf}
\end{center}

% New slide
\begin{frame}
\frametitle{Statements and questions}
Consider a problem with three mutually exclusive, exhaustive possibilities
$a$, $b$, and $c$. The lattice of statements is
